---
title: "Wild Git Collaboration Practice"
format: 
  html:
    code-fold: show
execute: 
  warning: false
  message: false
---
<<<<<<< HEAD
```{r}

library(ggplot2)
=======

```{r}

library(tidyverse)
library(janitor)
library(here)
>>>>>>> 109eb16169675e3b8a2ee0243ddd96044ec4eaf1

```


## STEP 5: No merge conflicts!

```{r partner 1}
### In this code chunk, start with the diamonds dataset (built in to
### ggplot2 package) and create a plot of price vs. carat (or some other
### variables of your choice)

<<<<<<< HEAD
=======
diamond_clean <- diamonds |>
  clean_names()



>>>>>>> 109eb16169675e3b8a2ee0243ddd96044ec4eaf1

```

```{r partner 2}
### In this code chunk, start with the diamonds dataset (built in to
### ggplot2 package) and create a subset based on filtering, e.g., 
### size greater than 1 carat or cut is "Ideal"

<<<<<<< HEAD
diamonds <- diamonds
=======

>>>>>>> 109eb16169675e3b8a2ee0243ddd96044ec4eaf1



```

## STEP 7: Uh oh, merge conflicts!

```{r break-it-1}
### Both partners - delete this comment, then write some code here
### to plot, summarize, calculate something simple using the diamonds
### dataset.


```

## STEP 11: And even more merge conflicts!

```{r break-it-2}
### Both partners - delete this comment, then write some code here
### to plot, summarize, calculate something simple using the diamonds
### dataset.


```

